---
title: "Alu"
output: html_notebook
---

```{r}
knitr::opts_knit$set(base.dir = "results")
knitr::opts_chunk$set(fig.path = "Alu/")
knitr::opts_chunk$set(dev="pdf")
knitr::opts_chunk$set(fig.show="hold")

library(data.table)
library(ggplot2)
library(gghighlight)
library(cowplot)
library(mgcv)

source("../functions.R")
```

```{r load_peaks}
zcw_peaks_cin <- fread("../data/peaks/SingleBasePeaks.WTCHG_538916_221156_vs_WTCHG_538916_217108_AND_WTCHG_538916_220144.p0.000001.sep250.ALL.bed")
zcw_peaks_cin <- prejoin(zcw_peaks_cin)

zcw_wP9_vs_chip_Z <- fread("../data/peaks/SingleBasePeaks.WTCHG_538916_223180_vs_WTCHG_538916_221156.p0.000001.sep250.ALL.bed")
zcw_wP9_vs_chip_Z <- prejoin(zcw_wP9_vs_chip_Z)

HP9N_peaks <- fread("../data/peaks/SingleBasePeaks.NA15-SRR5627138_AND_NA15-SRR5627139_vs_NA15-SRR5627140.p0.000001.sep250.ALL.bed")
HP9N_peaks <- prejoin(HP9N_peaks)

HP9combo_peaks <- fread("../data/peaks/SingleBasePeaks.NA15-SRR5627146_AND_NA15-SRR5627147_vs_NA15-SRR5627143.p0.000001.sep250.ALL.bed")
HP9combo_peaks <- prejoin(HP9combo_peaks)
```


Over half of all ZcwST peaks overlap Alu, overrepresented in low enrichment peaks. L1 also shows a pattern of being depleted at high enrichment peaks. Other repeats don't overlap a large fraction of preaks.

```{r Zcw_vs_repeats}
repeats <- fread("../data/repeats/Repeat_MaskerSorted.bed")

setnames(repeats, c("chr","CI_start","CI_stop","Name","Score","Strand"))

repeats$id <- seq_along(repeats$chr)

repeats <- prejoin(repeats, ext = 0)

# check order preserverd
stopifnot(sum(diff(repeats$id)<0)==0)
stopifnot(sum(diff(repeats$id)!=1)==0)

head(repeats[,.N,by=Name][order(-N)], 50)

fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[Name!="Alu"][grep("Alu",Name)][CI_stop-CI_start>250 & CI_stop-CI_start<350], x1="Zcw UT", y1="Alu Repeats", shift=1e8) # yes up to 70%
fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("L1",Name)], x1="Zcw UT", y1="L1 Repeats", shift=1e8) # depeated
fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("LTR",Name)], x1="Zcw UT", y1="LTR Repeats", shift=1e8) # not

fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("MIR",Name)], x1="Zcw UT", y1="MIR Repeats", shift=1e8) # not but higher in high enriched 12%
fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("MIR",Name)], x1="Zcw UT", y1="MIR Repeats", shift=1e8) + scale_y_continuous()
# fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("L2",Name)], x1="Zcw UT", y1="Repeats", shift=1e8) # not, 12%
# fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("\\(",Name)], x1="Zcw UT", y1="Repeats", shift=1e8) # not 12%
fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("\\(",Name)], x1="Zcw UT", y1="SimpleRepeats", shift=1e8) + scale_y_continuous()# 2% higher in low enriched
# fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("MER",Name)], x1="Zcw UT", y1="Repeats", shift=1e8) # not 10%
# fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("MLT",Name)], x1="Zcw UT", y1="Repeats", shift=1e8) # not 5%
# fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("FLAM",Name)], x1="Zcw UT", y1="Repeats", shift=1e8) # not <5%
# fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("THE",Name)], x1="Zcw UT", y1="Repeats", shift=1e8) # not <5%
# fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("L3",Name)], x1="Zcw UT", y1="Repeats", shift=1e8) # not <5%
# fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("rich",Name)], x1="Zcw UT", y1="Repeats", shift=1e8) # not
# fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("Charlie",Name)], x1="Zcw UT", y1="Repeats", shift=1e8) # not
# fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("Tigger",Name)], x1="Zcw UT", y1="Repeats", shift=1e8) # not
# fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("MST",Name)], x1="Zcw UT", y1="Repeats", shift=1e8) # not
# fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("Mam",Name)], x1="Zcw UT", y1="Repeats", shift=1e8) # not
# fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("HERV",Name)], x1="Zcw UT", y1="Repeats", shift=1e8) # not
# fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("ERVL",Name)], x1="Zcw UT", y1="Repeats", shift=1e8) # not
# fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[Name=="THE1B"], x1="Zcw UT", y1="Repeats", shift=1e8) # not
```

```{r zcw_vs_repeats_2}
fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("LTR",Name)], x1="Zcw UT", y1="LTR Repeats", shift=1e8) + scale_y_continuous()

fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[Name=="MIRb"], x1="Zcw UT", y1="LTR Repeats", shift=1e8) + scale_y_continuous()

fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[Name=="MIR"], x1="Zcw UT", y1="LTR Repeats", shift=1e8) + scale_y_continuous()

fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[Name=="L2a"], x1="Zcw UT", y1="LTR Repeats", shift=1e8) + scale_y_continuous()

fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[Name=="MIRc"], x1="Zcw UT", y1="LTR Repeats", shift=1e8) + scale_y_continuous()

fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[Name=="MIR3"], x1="Zcw UT", y1="LTR Repeats", shift=1e8) + scale_y_continuous()

fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[Name=="A-rich"], x1="Zcw UT", y1="LTR Repeats", shift=1e8) + scale_y_continuous()

fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[Name=="MER5A"], x1="Zcw UT", y1="LTR Repeats", shift=1e8) + scale_y_continuous()

fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[Name=="FLAM_C"], x1="Zcw UT", y1="LTR Repeats", shift=1e8) + scale_y_continuous() # enriched at low


fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("HAL1b",Name)], x1="Zcw UT", y1="LTR Repeats", shift=1e8) + scale_y_continuous()
```


```{r zcw_vs_repeats_3}
repeats[grep("THE1.-int",Name)]
repeats[, length := CI_stop-CI_start]
repeats$enrichment <- as.numeric(repeats$Score)
repeats$enrichment <- as.numeric(repeats$length)

plot(sort(repeats[grep("THE1.-int",Name)]$length))
fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("THE1.-int",Name)], x1="Zcw UT", y1="THE1X-int", shift=1e8)
fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("THE1.-int",Name)], x1="Zcwpw1", y1="THE1X-int", shift=1e8) + scale_y_continuous() + theme(legend.position = "bottom")

repeats$enrichment <- as.numeric(repeats$length)
fraction_overlapN2(repeats[grep("THE1.-int",Name)], zcw_peaks_cin, x1="THE1X-int", y1="Zcwpw1", shift=1e8) + scale_y_continuous() + scale_x_continuous() + theme(legend.position = "bottom") + xlab("THE1X-int length")

fraction_overlapN2(repeats[grep("MIR",Name)], zcw_peaks_cin, x1="MIR", y1="Zcwpw1", shift=1e8) + scale_y_continuous() + scale_x_continuous() + theme(legend.position = "bottom") + xlab("MIR length")


fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("MIR",Name)], x1="Zcwpw1 UT", y1="MIR Repeats", shift=1e8) + scale_y_continuous()

fraction_overlapN2(repeats[grep("MIR",Name)], zcw_peaks_cin, x1="MIR", y1="Zcw UT", shift=1e8) + scale_y_continuous() + scale_x_continuous()
```


Non Alu repeats are not enriched relative to expected based on randomised positions.

```{r zcw_vs_Alu_subtypes}

# Summary of those not enriched
fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("\\(|MIR|L2|THE1B|MER|MLT|FLAM|THE|L3|rich|Charlie|Tigger|LTR|MST|Mam|HERV|ERVL",Name)], x1="Zcw UT", y1="Non Alu Repeats", shift=1e8)

# Summary of what's left
fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[!grep("\\(|Alu|MIR|L2|L1|THE1B|MER|MLT|FLAM|THE|L3|rich|Charlie|Tigger|LTR|MST|Mam|HERV|ERVL",Name)], x1="Zcw UT", y1="Repeats", shift=1e8) # not




fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("AluJ",Name)], x1="Zcw UT", y1="Repeats", shift=1e8) # yes up to 0.2
fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("AluS",Name)], x1="Zcw UT", y1="Repeats", shift=1e8) # yes up to 0.55
fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("AluY",Name)], x1="Zcw UT", y1="Repeats", shift=1e8) # a bit
fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[Name=="Alu"], x1="Zcw UT", y1="Repeats", shift=1e8) # no

fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("AluSx",Name)], x1="Zcw UT", y1="Repeats", shift=1e8) # yes up to 0.25
fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("AluSz",Name)], x1="Zcw UT", y1="Repeats", shift=1e8) # yes up to 0.15
fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("AluSq",Name)], x1="Zcw UT", y1="Repeats", shift=1e8) # yes
fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("AluSp",Name)], x1="Zcw UT", y1="Repeats", shift=1e8) # yes
fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("AluSc",Name)], x1="Zcw UT", y1="Repeats", shift=1e8) # yes
fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("AluSg",Name)], x1="Zcw UT", y1="Repeats", shift=1e8) # yes

fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("AluSx",Name)], x1="Zcw UT", y1="Repeats", shift=1e8) + scale_y_continuous()
fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("AluSz",Name)], x1="Zcw UT", y1="Repeats", shift=1e8) + scale_y_continuous()
fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeats[grep("AluSg",Name)], x1="Zcw UT", y1="Repeats", shift=1e8) + scale_y_continuous()
```

## Fraction of Alu

75% of all Alu repeats have a ZcwST peak, higher for those with better match to consensus.

```{r fraction_of_Alu}

repeats$enrichment <- as.numeric(repeats$Score)
fraction_overlapN2(repeats[Name!="Alu"][grep("Alu",Name)][CI_stop-CI_start>250 & CI_stop-CI_start<350], zcw_peaks_cin, x1="Alu Repeats by SmithWaterman Score (Not ", y1="Zcw UT", shift=1e8) # 

# Only ~ 35% of ==Alu overlap Zcw
# fraction_overlapN2(repeats[Name=="Alu"], zcw_peaks_cin, x1="Zcw UT", y1="Repeats", shift=1e8)
```

## Prdm9 Peaks

As expected Prdm9 is enriched for THE1B - but only N term not C term. Neither set of Prdm9 peaks not enriched for Alu repeats.

```{r P9_Peaks_vs_repeats}
# P9 enriched in THE1B
fraction_overlapN2(HP9N_peaks[cov_input>=5], repeats[Name=="THE1B"], x1="HP9N", y1="THE1B", shift=1e8) + scale_y_continuous()
# not C term
fraction_overlapN2(HP9combo_peaks[cov_input>=5], repeats[Name=="THE1B"], x1="HP9 Cterm", y1="THE1B", shift=1e8) + scale_y_continuous()
# P9 Not enriched for Alu
fraction_overlapN2(HP9N_peaks[cov_input>=5], repeats[grep("Alu",Name)], x1="HP9N", y1="Alu Repeats", shift=1e8)
fraction_overlapN2(HP9combo_peaks[cov_input>=5], repeats[Name!="Alu"][grep("Alu",Name)], x1="HP9 Cterm HA + V5", y1="Alu Repeats", shift=1e8)
fraction_overlapN2(zcw_wP9_vs_chip_Z[cov_input>=5], repeats[Name!="Alu"][grep("Alu",Name)], x1="Zcw CVC", y1="Alu Repeats", shift=1e8)

# total = 5,607,738
# left = 230,099
# Alu = 1,209,364
repeats[!grep("\\(|Alu|MIR|L2|L1|THE1B|MER|MLT|FLAM|THE|L3|rich|Charlie|Tigger|LTR|MST|Mam|HERV|ERVL",Name)][,.N,by=Name][order(-N)][1:50]

repeats[grep("Alu",Name)][,.N,by=Name][order(-N)][1:50]

```

# CpG

```{r Alu_by_CpG, fig.width = 10, fig.height = 5.5}

AluRepeats <- seqinr::read.fasta("../data/repeats/AluRepeats.fa", forceDNAtolower = FALSE, as.string = TRUE)
AluRepeats <- unlist(AluRepeats)

repeatsAlu <- repeats[Name!="Alu"][grep("Alu",Name)][CI_stop-CI_start>250 & CI_stop-CI_start<350]
# check names match for ordering
all.equal(repeatsAlu[,paste0(Name,"(",Strand,")")], names(AluRepeats))
repeatsAlu$length <- nchar(AluRepeats)

CG_locations <- sapply(AluRepeats,function(x) stringr::str_locate_all(x,"cg")[[1]][,1])
repeatsAlu$CG_count <- sapply(CG_locations, length)



# location & frequency hist
hist(unlist(CG_locations[repeatsAlu$length==299]), breaks=1000)
hist(repeatsAlu$CG_count, breaks=50)

# % of Alu
repeatsAlu$enrichment <- repeatsAlu$CG_count

AluEnrich <- fraction_overlapN2(repeatsAlu, zcw_peaks_cin, x1="Alu Repeats by CpG Count (Not ", y1="Zcw UT", shift=1e9) + 
  scale_x_continuous() +
  xlim(0,25) + # min of 200 data points required
  xlab("CpG Count in Alu Repeats") + 
  ylab("Fraction of Alu Repeats overlaping\n ZCWPW1 peaks (no PRDM9)") +
  theme(legend.position = "bottom")


###### % of Zcw

tmp <- overlapGam(zcw_peaks_cin[cov_input>=5], repeats[Name!="Alu"][grep("Alu",Name)][CI_stop-CI_start>250 & CI_stop-CI_start<350])
tmpR <- overlapGam(zcw_peaks_cin[cov_input>=5], repeats[Name!="Alu"][grep("Alu",Name)][CI_stop-CI_start>250 & CI_stop-CI_start<350], shift = 1e8)

tmp2 <- fraction_overlapN2(zcw_peaks_cin[cov_input>=5], 
                           repeats[Name!="Alu"][grep("Alu",Name)][CI_stop-CI_start>250 & CI_stop-CI_start<350],
                           x1="Zcw UT", y1="Alu Repeats", shift=1e8) # yes up to 70%

pi <- tmp2 + 
  geom_ribbon(data=tmp, aes(ymin = Overlap - 2*se, ymax = Overlap + 2*se), fill = "#E41A1C", colour="#E41A1C", alpha=0.5) +
  geom_ribbon(data=tmpR, aes(ymin = Overlap - 2*se, ymax = Overlap + 2*se), fill = "#377EB8", colour="#377EB8", alpha=0.5) +
  scale_x_log10(limits=c(0.3,5)) +
  theme(legend.position = "bottom") +
  xlab("ZCWPW1 Enrichment (no PRDM9)") +
  ylab("Fraction of ZCWPW1 peaks that overlap Alu repeats")

pmain <- plot_grid(pi + theme(legend.position = "none"), AluEnrich + theme(legend.position = "none"), labels = "AUTO")

alu_enrich_plot <- plot_grid(pmain, get_legend(AluEnrich), ncol=1, rel_heights = c(1, 0.07))

#pdf("../results/Alu_by_CpG.pdf", width = 10, height = 5.5)
alu_enrich_plot
#dev.off()

# % of Zcw
fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeatsAlu[enrichment==0], x1="Zcw UT", y1="Alu Repeats CpG=0", shift=1e8) + scale_y_continuous()
fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeatsAlu[enrichment==1], x1="Zcw UT", y1="Alu Repeats CpG=1", shift=1e8) + scale_y_continuous()
fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeatsAlu[enrichment==5], x1="Zcw UT", y1="Alu Repeats CpG=5", shift=1e8) + scale_y_continuous()
fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeatsAlu[enrichment==10], x1="Zcw UT", y1="Alu Repeats CpG=10", shift=1e8) + scale_y_continuous()
fraction_overlapN2(zcw_peaks_cin[cov_input>=5], repeatsAlu[enrichment==20], x1="Zcw UT", y1="Alu Repeats CpG=20", shift=1e8) + scale_y_continuous()
```

```{r review_fig8, fig.width=12, fig.height=12}
zcw_wP9_peaks_cin <- fread("../data/peaks/SingleBasePeaks.WTCHG_538916_223180_vs_WTCHG_538916_217108_AND_WTCHG_538916_220144.p0.000001.sep250.ALL.bed")
zcw_wP9_peaks_cin <- prejoin(zcw_wP9_peaks_cin)

zcw_peaks_cin$HP9combo_enrichment <- foverlaps(zcw_peaks_cin, HP9combo_peaks, mult="first")$enrichment
zcw_wP9_peaks_cin$HP9combo_enrichment <- foverlaps(zcw_wP9_peaks_cin, HP9combo_peaks, mult="first")$enrichment

p1 <- fraction_overlapN2(zcw_wP9_peaks_cin[cov_input>=5], 
                           repeats[Name!="Alu"][grep("Alu",Name)][CI_stop-CI_start>250 & CI_stop-CI_start<350],
                           x1="ZCWPW1 (w PRDM9)\n [inc PRDM9 sites]", y1="Alu Repeats", shift=1e8) # yes up to 70%

p2 <- fraction_overlapN2(zcw_peaks_cin[cov_input>=5], 
                           repeats[Name!="Alu"][grep("Alu",Name)][CI_stop-CI_start>250 & CI_stop-CI_start<350],
                           x1="ZCWPW1 (w/o PRDM9)\n [inc PRDM9 sites]", y1="Alu Repeats", shift=1e8) # yes up to 70%

p3 <- fraction_overlapN2(zcw_wP9_peaks_cin[cov_input>=5][is.na(HP9combo_enrichment)], 
                           repeats[Name!="Alu"][grep("Alu",Name)][CI_stop-CI_start>250 & CI_stop-CI_start<350],
                           x1="ZCWPW1 (w PRDM9)\n [excluding PRDM9 sites]", y1="Alu Repeats", shift=1e8) # yes up to 70%

p4 <- fraction_overlapN2(zcw_peaks_cin[cov_input>=5][is.na(HP9combo_enrichment)], 
                           repeats[Name!="Alu"][grep("Alu",Name)][CI_stop-CI_start>250 & CI_stop-CI_start<350],
                           x1="ZCWPW1 (w/o PRDM9)\n [excluding PRDM9 sites]", y1="Alu Repeats", shift=1e8) # yes up to 70%

plot_grid(p1, p2, p3, p4)
```


```{r}
repeatsAlu$id <- seq_along(repeatsAlu$chr)

overlapingAluIDS <- foverlaps(zcw_peaks_cin, repeatsAlu, mult="first")$id
overlapingAluIDS2 <- overlapingAluIDS[!is.na(overlapingAluIDS)]

repeatsAlu$overlap <- FALSE
repeatsAlu[id %in% overlapingAluIDS2, overlap := TRUE]

# compare count of CpG
repeatsAlu$enrichment <- repeatsAlu$CG_count
ggplot(repeatsAlu, aes(enrichment, fill=overlap)) + geom_histogram(aes(y=..density..), position = "identity", alpha=0.7, bins=70) + scale_fill_brewer(palette = "Set1")
ggplot(repeatsAlu, aes(length, colour=overlap)) + geom_density()

# compare location of CpG
hist(unlist(CG_locations[repeatsAlu[overlap==TRUE]$id]), breaks=1000)
hist(unlist(CG_locations[repeatsAlu[overlap==FALSE]$id]), breaks=1000)

# compare proportion of Alu families
AluOverapProp <- merge(repeatsAlu[overlap==TRUE][,.(Overlap=.N/nrow(repeatsAlu[overlap==TRUE]), Number=.N),by=Name],
                       repeatsAlu[overlap==FALSE][,.(NonOverlap=.N/nrow(repeatsAlu[overlap==FALSE]), Number=.N),by=Name], by="Name")
AluOverapProp[, ratioOfProportions := (Overlap+0.01)/(NonOverlap+0.01)]
AluOverapProp[, Occurrences := Number.y + Number.x]

ggplot(AluOverapProp, aes(Name, ratioOfProportions, size=Occurrences)) +
  geom_hline(yintercept = 1, col="darkgrey") +
  geom_point() +
  coord_flip() +
  scale_size() +
  scale_y_log10()


# compare proportion of GC Counts
AluOverapProp <- merge(repeatsAlu[overlap==TRUE][,.(Overlap=.N/nrow(repeatsAlu[overlap==TRUE]), Number=.N),by=CG_count],
                       repeatsAlu[overlap==FALSE][,.(NonOverlap=.N/nrow(repeatsAlu[overlap==FALSE]), Number=.N),by=CG_count], by="CG_count")
AluOverapProp[, ratioOfProportions := (Overlap)/(NonOverlap)]
AluOverapProp[, Occurrences := Number.y + Number.x]

ggplot(AluOverapProp, aes(CG_count, ratioOfProportions, size=Occurrences)) +
  geom_hline(yintercept = 1, col="darkgrey") +
  geom_point() +
  scale_size() +
  scale_y_log10()

# AluOverapProp$Type <- reorder(AluOverapProp$Name, AluOverapProp$ratioOfProportions)
# ggplot(AluOverapProp, aes(Type, ratioOfProportions, size=count)) + geom_hline(yintercept = 1, col="darkgrey") + geom_point() + coord_flip() + scale_size() + scale_y_log10()


# p <- ggplot(AluOverapProp, aes(Overlap, NonOverlap, label=Name, colour=log(ratioOfProportions))) + 
#   #stat_smooth(method="lm", formula = y ~ 0 + x, se = F, col="grey", size=1) +
#   geom_abline() +
#   geom_point() + 
#   scale_x_log10() + scale_y_log10()
# 
# p
# p + scale_x_continuous() + scale_y_continuous() + geom_label_repel(data=AluOverapProp[ratioOfProportions<0.9 | ratioOfProportions>1.5])
# ggplot(AluOverapProp, aes(V1.x*V1.y, V1.x/V1.y, label=Name, colour=ratioOfProportions)) + geom_point() + geom_label_repel(data=AluOverapProp[ratioOfProportions<0.7 | ratioOfProportions>1.5]) + scale_x_log10() + scale_y_log10()
```

Cross check results
```{r cross_check}
repeatsAlu$enrichment <- as.numeric(repeatsAlu$Score)
fraction_overlapN2(repeatsAlu[grep("AluJ",Name)], zcw_peaks_cin, x1="AluJ Repeats by SmithWaterman Score (Not ", y1="Zcw UT", shift=1e8) + scale_x_continuous()
fraction_overlapN2(repeatsAlu[grep("AluSz",Name)], zcw_peaks_cin, x1="AluSz Repeats by SmithWaterman Score (Not ", y1="Zcw UT", shift=1e8) + scale_x_continuous() 
fraction_overlapN2(repeatsAlu[grep("AluS[cqpgx]",Name)], zcw_peaks_cin, x1="AluS[cqpgx] Repeats by SmithWaterman Score (Not ", y1="Zcw UT", shift=1e8) + scale_x_continuous()
fraction_overlapN2(repeatsAlu[grep("AluY",Name)], zcw_peaks_cin, x1="AluY Repeats by SmithWaterman Score (Not ", y1="Zcw UT", shift=1e8) + scale_x_continuous()
```

```{r score_&_CGcount}
repeatsAlu[grep("AluJ",Name), class := "AluJ"]
repeatsAlu[grep("AluSz",Name), class := "AluSz"]
repeatsAlu[grep("AluS[qpgx]",Name), class := "AluS[qpgx]"]
repeatsAlu[grep("AluSc",Name), class := "AluSc"]
repeatsAlu[grep("AluY",Name), class := "AluY"]

ggplot(repeatsAlu, aes(Score, color=class)) + geom_density()

ggplot(repeatsAlu, aes(CG_count)) + geom_histogram(binwidth = 1) + facet_wrap(~class, scales='free_y')
```

# CpG in general

Does CpG presence/number affect mean enrichment for non Alus?

```{r Cpg_general, fig.width=10}

rand_cpg <- fread("../data/peaks/Zcw_random_CpGcount.bed") #"~/Downloads/chr1_random_CpGcount.bed")
# mean(rand_cpg$V7) = 2.817 - close!
setnames(rand_cpg, c("chr","CI_start_ext","CI_stop_ext","x","width","strand","CpGcount"))

zcw_at_rand_cpg <- fread("../data/peaks/ForceCalledPeaks_WTCHG_538916_221156_vs_WTCHG_538916_217108_AND_WTCHG_538916_220144_AT_Zcw_random.bed.bed")

rand_cpg <- merge(rand_cpg,zcw_at_rand_cpg, by.x=c("chr","CI_start_ext"), by.y=c("chr","center_start"))

zcw_peaks_cin_cpg <- fread("../data/peaks/SingleBasePeaks.WTCHG_538916_221156_vs_WTCHG_538916_217108_AND_WTCHG_538916_220144.p0.000001.sep250.ALL_wCpGcount.bed")
names(zcw_peaks_cin_cpg)[1:11] <- c("chr", "center_start", "center_stop", "CI_start", "CI_stop", "cov_r1", "cov_r2", "cov_input", "enrichment", "likelihood", "pvalue")
names(zcw_peaks_cin_cpg)[12] <- "CpGcount"
zcw_peaks_cin_cpg <- prejoin(zcw_peaks_cin_cpg, width=0)
cor(zcw_peaks_cin_cpg$enrichment, zcw_peaks_cin_cpg$CpGcount)

zcw_wP9_vs_chip_Z_cpg <- fread("../data/peaks/SingleBasePeaks.WTCHG_538916_223180_vs_WTCHG_538916_221156.p0.000001.sep250.ALL_wCpGcount.bed")
names(zcw_wP9_vs_chip_Z_cpg)[1:12] <- c("chr", "center_start", "center_stop", "CI_start", "CI_stop", "cov_r1", "cov_r2", "cov_input", "enrichment", "likelihood", "pvalue","CpGcount")
zcw_wP9_vs_chip_Z_cpg <- prejoin(zcw_wP9_vs_chip_Z_cpg, width=0)


zcw_peaks_cin_cpg_alu <- foverlaps(zcw_peaks_cin_cpg, repeatsAlu, mult = "first")
zcw_peaks_cin_cpg_repeats <- foverlaps(zcw_peaks_cin_cpg, repeats, mult = "first")
setkey(rand_cpg, chr, CI_start_ext, CI_stop_ext)
rand_cpg_alu <- foverlaps(rand_cpg, repeatsAlu, mult = "first")

# non Alus
cpg_table <- rbind(data.table(table(rand_cpg_alu[is.na(Name)]$CpG), type="Randomised Peaks"),
      data.table(table(zcw_peaks_cin_cpg_alu[is.na(Name)]$CpGcount), type="Observed Peaks"))

ggplot(cpg_table, aes(as.numeric(V1), N, fill=type)) +
  geom_col(position="dodge") +
  xlim(-1,20) +
  scale_fill_brewer(palette = "Set1") +
  labs(x="Count of CpGs under peak +/-150", y="Frequency")

# Alus
cpg_table <- rbind(data.table(table(rand_cpg_alu[!is.na(Name)]$CpG), type="Randomised Peaks"),
      data.table(table(zcw_peaks_cin_cpg_alu[!is.na(Name)]$CpGcount), type="Observed Peaks"))

ggplot(cpg_table, aes(as.numeric(V1), N, fill=type)) +
  geom_col(position="dodge") +
  xlim(-1,20) +
  scale_fill_brewer(palette = "Set1") +
  labs(x="Count of CpGs under peak +/-150", y="Frequency")

###

zcw_peaks_cin_cpg[CpGcount==0][order(-enrichment)][cov_input>5]
cor.test(zcw_peaks_cin_cpg[cov_input>5]$enrichment, zcw_peaks_cin_cpg[cov_input>5]$CpGcount)

plot(zcw_peaks_cin_cpg[cov_input>5]$CpGcount, zcw_peaks_cin_cpg[cov_input>5]$enrichment)

# overall
tmp <- zcw_peaks_cin_cpg[cov_input>5][,.(MeanEnrich=mean(enrichment),.N),by=CpGcount][order(CpGcount)]
qplot(tmp$CpGcount, tmp$MeanEnrich) # has an uptick at the start (due to diff composition of Alu's)

#zcw_peaks_cin_cpg_repeats[Repeat == "L1M", .N, by=Name][order(-N)]

# all repeats
zcw_peaks_cin_cpg_repeats[is.na(Name), Repeat := "Non Repeat"]
zcw_peaks_cin_cpg_repeats[!is.na(Name), Repeat := "Other Repeat"]
zcw_peaks_cin_cpg_repeats[grep("^Alu",Name), Repeat := "Alu"]
#zcw_peaks_cin_cpg_repeats[grep("^L1",Name), Repeat := "L1"]

#zcw_peaks_cin_cpg_repeats[grep("^L1M",Name), Repeat := "L1M"], remove for simplicity

zcw_peaks_cin_cpg_repeats[grep("^L1M[1-3]|^L1MA",Name), Repeat := "L1M1-3 or L1MA"]
# zcw_peaks_cin_cpg_repeats[grep("^L1M4",Name), Repeat := "L1M4"]
# zcw_peaks_cin_cpg_repeats[grep("^L1M5",Name), Repeat := "L1M5"]
# zcw_peaks_cin_cpg_repeats[grep("^L1M6",Name), Repeat := "L1M6"]

#zcw_peaks_cin_cpg_repeats[grep("^L1MA",Name), Repeat := "L1MA"] # now included in above or

#zcw_peaks_cin_cpg_repeats[grep("^L1MD",Name), Repeat := "L1MD"]
# zcw_peaks_cin_cpg_repeats[grep("^L1MB",Name), Repeat := "L1MB"]
# zcw_peaks_cin_cpg_repeats[grep("^L1MC",Name), Repeat := "L1MC"]
# zcw_peaks_cin_cpg_repeats[grep("^L1ME",Name), Repeat := "L1ME"]

zcw_peaks_cin_cpg_repeats[grep("^L1P",Name), Repeat := "L1P"]
#zcw_peaks_cin_cpg_repeats[grep("^L1PR",Name), Repeat := "L1PR"] # big change, but don't show to simplify
# zcw_peaks_cin_cpg_repeats[grep("^L1PA",Name), Repeat := "L1PA"]
# zcw_peaks_cin_cpg_repeats[grep("^L1PB",Name), Repeat := "L1PB"]


# zcw_peaks_cin_cpg_repeats[grep("L2",Name), Repeat := "L2"]
# zcw_peaks_cin_cpg_repeats[grep("MIR",Name), Repeat := "MIR"]
# zcw_peaks_cin_cpg_repeats[grep("MER",Name), Repeat := "MER"]
# zcw_peaks_cin_cpg_repeats[grep("LTR",Name), Repeat := "LTR"]
# zcw_peaks_cin_cpg_repeats[grep("THE",Name), Repeat := "THE"]
# zcw_peaks_cin_cpg_repeats[grep("HER",Name), Repeat := "HER"]
# zcw_peaks_cin_cpg_repeats[grep("MST",Name), Repeat := "MST"]




tmp <- zcw_peaks_cin_cpg_repeats[cov_input>5][,.(MeanEnrich=mean(i.enrichment),.N, sd=sd(i.enrichment)),by=c("CpGcount","Repeat")][order(CpGcount)]

CpGgeneral <- ggplot(tmp, aes(CpGcount, MeanEnrich, colour=Repeat, size=N)) +
  geom_point() +
  scale_color_brewer(palette = "Set1") +
  xlim(0,20) +
  ylim(0.8, 2.5) +
  geom_line(size=0.5, linetype="dashed") +
  theme_minimal() +
  geom_pointrange(aes(ymin=MeanEnrich - 2*(sd/sqrt(N)), ymax=MeanEnrich + 2*(sd/sqrt(N))), size=0.5) +
  ylab("Mean Enrichment of Zcwpw1 peaks (without Prdm9)") +
  xlab("Count of CpGs under peak +/-150")

#pdf("../results/CpG_general.pdf", width=10)
CpGgeneral
#dev.off()

tmp <- cbind(data.table(table(rand_cpg_alu[!is.na(Name)]$CpG), type="Randomised Peaks"),
      data.table(table(zcw_peaks_cin_cpg_alu[!is.na(Name)]$CpGcount), type="Observed Peaks"))
tmp <- tmp[1:25]
tmp2 <- cbind(data.table(table(rand_cpg_alu[is.na(Name)]$CpG), type="Randomised Peaks"),
      data.table(table(zcw_peaks_cin_cpg_alu[is.na(Name)]$CpGcount), type="Observed Peaks"))
tmp2 <- tmp2[1:25]
tmp$isAlu <- T
tmp2$isAlu <- F
tmp <- rbind(tmp, tmp2)
setnames(tmp, c("CpGCount","NRand","t1","v1","NObs","t2","isAlu"))

tmp$CpGCount <- as.numeric(tmp$CpGCount)
ggplot(tmp, aes(CpGCount, NObs/NRand, colour=isAlu)) + geom_point()

p2 <- ggplot(tmp, aes(CpGCount, NObs/NRand, colour=isAlu)) + geom_point() + scale_y_log10() + ylab("Observed Peaks : Randomised Peaks") + scale_color_brewer(palette = "Set1") + theme(legend.position = "bottom")

#pdf("../results/Cpg_general2.pdf")
p2
#dev.off()

```


# Proportion of Zcw peaks by CpG count


```{r}
hist(zcw_wP9_vs_chip_Z_cpg[cov_input>5]$CpGcount, breaks=1000, xlim=c(-1,30))
hist(rand_cpg[cov_input>5]$CpGcount, breaks=1000, xlim=c(-1,30))
```


```{r CpG_Proportions, fig.width = 7, fig.height = 5}

zcw_peaks_cin_cpg2 <- zcw_peaks_cin_cpg[cov_input>5]
setorder(zcw_peaks_cin_cpg2, enrichment)

zcw_peaks_cin_cpg2$bin <- cut(1:nrow(zcw_peaks_cin_cpg2), 35)

binned_cpg_prop <- zcw_peaks_cin_cpg2[,.(enrichment=mean(enrichment),
                                        CpG_0=mean(CpGcount==0),
                     CpG_1=mean(CpGcount==1),
                     CpG_2_3=mean(CpGcount>=2 & CpGcount<=3),
                     CpG_4_6=mean(CpGcount>=4 & CpGcount<=6),
                     CpG_7_9=mean(CpGcount>=7 & CpGcount<=9),
                     CpG_10_12=mean(CpGcount>=10 & CpGcount<=12),
                     CpG_13gt=mean(CpGcount>=13)),
                  by=bin]

binned_cpg_prop <- melt(binned_cpg_prop, id.vars=c("bin","enrichment"))

cpg_prop_rand <- rand_cpg[cov_input>5,.(
                 CpG_0=mean(CpGcount==0),
                     CpG_1=mean(CpGcount==1),
                     CpG_2_3=mean(CpGcount>=2 & CpGcount<=3),
                     CpG_4_6=mean(CpGcount>=4 & CpGcount<=6),
                     CpG_7_9=mean(CpGcount>=7 & CpGcount<=9),
                     CpG_10_12=mean(CpGcount>=10 & CpGcount<=12),
                     CpG_13gt=mean(CpGcount>=13))]

cpg_prop_rand <- melt(cpg_prop_rand)
cpg_prop_rand$enrichment=-0.5
cpg_prop_rand$bin="Random"

# ggplot(binned_cpg_prop, aes(bin, -value, fill=variable)) +
#   geom_col(width=1) +
#   scale_fill_brewer()

tmp <- rbind(binned_cpg_prop, cpg_prop_rand)

tmp$CpG <- gsub("CpG_","",tmp$variable)
tmp$CpG <- gsub("_"," to ",tmp$CpG)
tmp$CpG <- gsub("gt"," >=",tmp$CpG)
tmp$CpG <- factor(tmp$variable, levels = tmp$variable, labels=tmp$CpG)

# reorder so 0 at bottom
tmp$CpG <- forcats::fct_rev(tmp$CpG)

# if the width is too big, the right column overlaps the left
# meaning the center of the col is no longer the mean enrichment
tmp[,diffnext := c(diff(enrichment),0.5), by=CpG]
tmp[,diffprev := c(0.5,diff(enrichment)), by=CpG]
tmp[diffnext<0, diffnext := 1]
tmp[diffprev<0, diffprev := 1]
tmp[,maxwidth := min(c(diffnext,diffprev)), by=c("bin","enrichment")]

CpG_Proportions <- ggplot(tmp, aes(enrichment, value, fill=CpG)) +
  geom_col(aes(width=maxwidth)) +
  scale_fill_brewer() +
  scale_x_continuous(labels=c("Random \n Peaks",0:5), breaks=c(-0.5,0:5)) +
  scale_fill_brewer(direction = -1, palette = "RdBu") +
  ylab("Proportion of ZCWPW1 Peaks") +
  xlab("Enrichment of ZCWPW1") +
  labs(fill="Number\nof CpGs")

CpG_Proportions
#ggsave("../results/CpG_Proportions.pdf", CpG_Proportions, width = 7, height = 5)

# to help with choosing bins
hist(zcw_peaks_cin_cpg$CpGcount, breaks=300, xlim=c(-1,20))

```

```{r check_geom_col}
ggplot(data.table(a=c(1,1,2,2),b=c(0.1,0.9,0.5,0.5),c=c(1,2,1,2)), aes(a,b, fill=c)) + geom_col()
ggplot(data.table(a=c(1,1,2,2),b=c(0.1,0.9,0.5,0.5),c=c(1,2,1,2)), aes(a,b, fill=c)) + geom_col(width=1)
ggplot(data.table(a=c(1,1,2,2),b=c(0.1,0.9,0.5,0.5),c=c(1,2,1,2)), aes(a,b, fill=c)) + geom_col(width=2)
ggplot(data.table(a=c(1,1,2,2),b=c(0.1,0.9,0.5,0.5),c=c(1,2,1,2)), aes(a,b, fill=c)) + geom_col(aes(width=a))
```

```{r CpG_plot, fig.height=10, fig.width=10}
#CpG_bottom <- plot_grid(CpGgeneral, CpG_Proportions, labels=c("C","D"), rel_widths = c(6,5))

CpGWindows <- readRDS("../data/CpG/NormalPeaks300bp.rds")

#pdf("../results/CpG_plot.pdf", height = 10, width = 10)
plot_grid(pi, CpGWindows + ylab("Probability of window overlaping a ZCWPW1 peak"), AluEnrich, CpG_Proportions + theme_minimal(), nrow=2, rel_widths = c(2,3), labels = c("A","C","B","D"))
#dev.off()
```


```{bash, eval=FALSE}
# format for IGV
tail -n +2 SingleBasePeaks.WTCHG_538916_223180_vs_WTCHG_538916_217108_AND_WTCHG_538916_220144.p0.000001.sep250.ALL.bed | cut -f 1-3 > SingleBasePeaks.WTCHG_538916_223180_vs_WTCHG_538916_217108_AND_WTCHG_538916_220144.p0.000001.sep250.ALL_headless.bed

tail -n +2 ../results/peaks/SingleBasePeaks.SRA_Altemose2015_SRR5627146_AND_SRA_Altemose2015_SRR5627147_vs_SRA_Altemose2015_SRR5627143.p0.000001.sep250.ALL.bed | cut -f 1-3 > ../results/peaks/SingleBasePeaks.SRA_Altemose2015_SRR5627146_AND_SRA_Altemose2015_SRR5627147_vs_SRA_Altemose2015_SRR5627143.p0.000001.sep250.ALL_headless.bed

tail -n +2 ../results/peaks/SingleBasePeaks.SRA_Altemose2015_SRR5627148_vs_SRA_Altemose2015_SRR5627142.p0.000001.sep250.ALL.bed | cut -f 1-3 > ../results/peaks/SingleBasePeaks.SRA_Altemose2015_SRR5627148_vs_SRA_Altemose2015_SRR5627142.p0.000001.sep250.ALL_headless.bed

tail -n +2 ../results/peaks/SingleBasePeaks.SRA_Altemose2015_SRR5627152_AND_SRR5627153_vs_SRA_Altemose2015_SRR5627143.p0.000001.sep250.ALL.bed | cut -f 1-3 > ../results/peaks/SingleBasePeaks.SRA_Altemose2015_SRR5627152_AND_SRR5627153_vs_SRA_Altemose2015_SRR5627143.p0.000001.sep250.ALL_headless.bed

#http://genome.ucsc.edu/cgi-bin/hgTables?db=hg38&hgta_group=hub_213889&hgta_track=hub_213889_Umap_24_quantitative&hgta_table=hub_213889_Umap.24.quantitative&hgta_doSchema=describe+table+schema
```


#What's enriched at Alus

```{bash, eval=FALSE}
tmp <- fread("grep -v '#' repeats/Alu_meta299.txt")
tmpIn <- fread("grep -v '#' repeats/Alu_meta_In299.txt")

AluK36 <- fread("grep -v '#' repeats/Alu_UT_H3K36me3.txt")
AluK4 <- fread("grep -v '#' repeats/Alu_UT_H3K4me3.txt")
tmpIn <- fread("grep -v '#' repeats/Alu_UT_input.txt")


a <- fread("FragPos/Fragment_Position_WTCHG_538916_221156.total")
b <- fread("FragPos/Fragment_Position_WTCHG_538916_217108.total")

AluK36_tot <- fread("FragPos/Fragment_Position_NA15-SRR5627148.total")
AluK4_tot <- fread("FragPos/Fragment_Position_NA15-SRR5627150_AND_NA15-SRR5627151.total") # approx
Alu_UTin_tot <- fread("FragPos/Fragment_Position_NA15-SRR5627142.total")


# K36 slightly enriched
plot((AluK36$V2 / tmpIn$V2) * (Alu_UTin_tot$V1 / AluK36_tot$V1), type="l", )
dev.off()

# K4 depleted
plot((AluK4$V2 / tmpIn$V2) * (Alu_UTin_tot$V1 / AluK4_tot$V1), type="l")
dev.off()
```

